\documentclass[11pt,twoside,openright,titlepage]{ce}

% =Imports===============================================================================
\usepackage[]{tcolorbox}
\usepackage[]{amsmath,amssymb,amsthm}
\usepackage[]{graphicx}
\usepackage[]{color}
\usepackage[]{listings}
\usepackage[]{hyperref}
\usepackage[]{nielstex}
\usepackage[]{nielsformat}
\usepackage[]{tikz}
\usepackage[]{tikz-3dplot}


% =Definitions===========================================================================
% Thesis specific definitions
\newcommand{\za}{\mathcal{A}}
\newcommand{\zb}{\mathcal{B}}
\newcommand{\zz}{\mathcal{Z}}

% =Document Attributes===================================================================
\msctitle{Sound Zones with a Cost Function based on Human Hearing}
\mscsubtitle{Subtitle Compulsory?}
\msckeywords{perceptual sound zones, sound field control, perceptual models, pressure matching}
\mscauthor{Niels Evert Marinus de Koeijer B.Sc.}
\msccity{Delft}
\msccountry{The Netherlands}
\mscnumber{??}
\mscdate{September 15, 2021}
\major{Electrical Engineering}
\mscinstitute{Delft University of Technology}
\mscfaculty{Electrical Engineering, Mathematics and Computer Science}
\mscdepartment{Microelectronics \& Computer Engineering}
\mscgroup{Circuits and Systems}
\chairperson{dr.ir. R.C. Hendriks}
\advisorone{dr. M. Bo M\o ller}
\advisortwo{dr. P. Martinez Nuevo}
\memberone{dr. M. Mastrangeli}
\membertwo{dr. J. Martinez Castañeda}

% =Abstract==============================================================================
\def\ABSTRACT{\todo{Currently, this contains the draft of my thesis. 
Everything and anything can be changed as far as I'm concerned, I appreciate all feedback!}}

% =Document==============================================================================
\begin{document}

% =Front Pages===========================================================================
\frontmatter
\makecover
\maketitle
\makesignature
\include{abstract}
\include{ack}
\tableofcontents
\listoffigures
\listoftables
\mainmatter

% =Content===============================================================================
\chapter{Introduction}
\label{sec:introduction}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{introduction/skeleton.tex}
\end{tcolorbox}
\newpage

\chapter{Review of Perceptual Model Literature}
\label{sec:literature_review_perceptual_models}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{literature_review_perceptual_models/skeleton.tex}
\end{tcolorbox}
\newpage
% \input{sound_zones/introduction.tex}

\chapter{Implementation of Perceptual Model}
\label{sec:perceptual_models}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{implementation_perceptual_models/skeleton.tex}
\end{tcolorbox}
\newpage
% \input{perceptual_models/introduction.tex}

\chapter{Review of Sound Zone Algorithms Literature}
\label{sec:literature_review_sound_zones}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{literature_review_sound_zones/skeleton.tex}
\end{tcolorbox}
\newpage
% \input{sound_zones/introduction.tex}

\chapter{Implementation of Reference Sound Zone Algorithm}
\label{sec:sound_zones}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{implementation_sound_zones/skeleton.tex}
\end{tcolorbox}
\newpage
\input{implementation_sound_zones/introduction.tex}
\newpage
\input{implementation_sound_zones/data_model.tex}
\newpage
\input{implementation_sound_zones/pressure_matching.tex}
\newpage
\input{implementation_sound_zones/frame_based_framework.tex}
\newpage
\input{implementation_sound_zones/frequency_domain_approach.tex}

\chapter{Implementation of Perceptual Sound Zone Algorithm}
\label{sec:perceptual_sound_zones}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{implementation_perceptual_sound_zones/skeleton.tex}
\end{tcolorbox}
\newpage
\input{implementation_perceptual_sound_zones/introduction.tex}
\newpage
\input{implementation_perceptual_sound_zones/perceptual_minimization.tex}
\newpage
\input{implementation_perceptual_sound_zones/perceptual_constraining.tex}

\chapter{Evaluation of Perceptual Sound Zone Algorithm}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\input{evaluation_perceptual_sound_zones/skeleton.tex}
\end{tcolorbox}

\chapter{Conclusion}
\begin{tcolorbox}
\section*{Skeleton of Chapter}
\newpage
\input{conclusion/skeleton.tex}
\end{tcolorbox}

\bibliography{bibliography}
\bibliographystyle{ieeetr}

% =Appendix==============================================================================
\appendix
\end{document}
